Bow shocks, bow waves, and dust waves

### 2019-01-14 papers/Papers1234/sec-dust-case-studies.tex
Fancy SED graph for LP Ori
Separate out the Orion observational material into new paper!

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ney-allen-sed}
  \caption{Infrared spectral energy distribution of the Ney--Allen
    nebula that surrounds \thD. }
  \label{fig:ney-allen-sed}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/lp-ori-sed}
  \caption{Optical/infrared spectral energy distribution of the LP Ori
    and associated nebula. }
  \label{fig:lp-ori-sed}
\end{figure}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "dusty-bow-wave"
%%% End:

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/ney-allen-sed-edited}
  \caption{Ultraviolet-to-infrared spectral energy distribution of the Ney--Allen
    nebula that surrounds \thD. }
  \label{fig:ney-allen-sed}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/lp-ori-sed-edited}
  \caption{Ultraviolet-to-infrared spectral energy distribution of LP~Ori
    and associated nebula. }
  \label{fig:lp-ori-sed}
\end{figure*}

@@

% Model shell-R001-n27-LP_Ori20Bz5 from cloudy-dust-charging
The Cloudy model for LP Ori

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "two-orions-bow"
%%% End:
